Adversarial State Aggregation

### 2019-11-05 minutia/paper/paper.tex
paper updated

    \subsection{Objective}
    The ultimate goal is deceiving the model either in choosing the worst possible action in an RL task or misclassifying an input in a classification task in a way which is not perceptible for unaided eye. In terms of a Markovian RL task we show how minimum set of worst-case actions are needed to result in the minimum final reward. We try to show that the model is not robust to other configuration of each benchmarks with different dynamics.

>>>>

    \subsection{Objective}
    The aggregate problem is stochastic even if the original problem is deterministic. Once we lay out the aggregate
    problem framework we can solve the problem by any exact methods either value- or policy-space solutions.

    The ultimate goal is deceiving the model either in choosing the worst possible action in an RL task or misclassifying an input in a classification task in a way which is not perceptible for unaided eye. In terms of a Markovian RL task we show how minimum set of worst-case actions are needed to result in the minimum final reward. We try to show that the model is not robust to other configuration of each benchmarks with different dynamics.
